---
name: "Jacobo Blanco"
position: "Data Scientist"
address: "Raffine #205, Toyotamakita 1-10-2, Nerima, Tokyo, 172-0016"
phone: "+817043000544"
www: "jayblanco.com"
email: "jayb88@gmail.com"
linkedin: "jacoboblanco"
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
params:
  data_dir: "raw-data/"
  n_roles_include: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(lubridate)
library(vitae)
library(glue)

source("r/formatters.R")

data_dir <- params$data_dir
n_roles_include <- params$n_roles_include
skip_roles <- c("Interac")
```

```{r}
work_entries <- read_csv(paste0(data_dir, "work.csv"))
education_entries <- read_tsv(paste0(data_dir, "education.csv"))
volunteer_entries <- read_tsv(paste0(data_dir, "volunteer.csv"))
award_entries <- read_tsv(paste0(data_dir, "awards.csv"))
```


## Profile

Data scientist with a strong background in analytics and modelling, as well as building tools and reports to help people get their job done better based on data. Passionate about communicating insights from data analysis to non-technical audiences and building tools to make people's work faster and easier. I also make really good ice coffee. For more detailed information on projects and sample materials please see the LinkedIn profile above.

## Work Experience

```{r}
work_entries %>%
  filter(job_id <= n_roles_include) %>%
  mutate(why = if_else(with %in% skip_roles, NA_character_, why)) %>%
  detailed_entries(what = what,
    when = build_date_range(start_date, end_date),
    where = build_location(city, country), why = why, with = with)
```

```{r}
work_entries %>%
  filter(job_id > n_roles_include) %>%
  mutate(why = NaN) %>%
  detailed_entries(
    what = what,
    when = build_date_range(start_date, end_date),
    where = build_location(city, country),
    with = with
  )
```
\newpage
## Education

```{r}
education_entries %>%
  detailed_entries(what = what, when = when, where = where, why = why, with = with)
```

## Volunteering

```{r}
volunteer_entries %>%
  detailed_entries(what = what, when = when, where = where, why = why, with = with)
```

## Awards and Honors

```{r}
award_entries %>%
  detailed_entries(what = what, when = when, where = where, why = why, with = with)
```

## Technical Skills

* Languages: R, Python, c++, bash
* Data visualization and reporting: ggplot2, shiny, plotly, rmarkdown, LaTeX
* Analysis and Machine learning: outlier detection, clustering, classification
* Software: Git and GitHub, RStudio, Sublime Text, JIRA, Confluence

## LANGUAGE SKILLS

* Spanish: First language
* English: Fluent, technical
* Hebrew: Fluent
* Japanese: Beginner
