---
name: "Jacobo Blanco"
position: "Data Scientist"
address: "Raffine #205, Toyotamakita 1-10-2, Nerima, Tokyo, 172-0016"
phone: "+817043000544"
www: "jayblanco.com"
email: "jayb88@gmail.com"
linkedin: "jacoboblanco"
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
data_dir: 'data/'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(lubridate)
library(vitae)

data_dir <– params$data_dir
```

## Profile

Data scientist with a strong background in real-world data analysis in a variety of contexts. A strong self-learner that quickly leverages new knowledge to tackle complex problems and provide value. Passionate about communicating insights from data analysis to non-technical audiences, and creating tools to make people's work faster and easier. For more detailed information on projects and sample materials please see the LinkedIn profile above.

## Work Experience

```{r}
read_tsv(paste0(data_dir, paste0(data_dir, "work.csv")) %>%
  detailed_entries(what = what, when = when, where = where, why = why, with = with)
```

## Education

```{r}
read_tsv(paste0(data_dir, "education.csv") %>%
  detailed_entries(what = what, when = when, where = where, why = why, with = with)
```

## Volunteering

```{r}
read_tsv(paste0(data_dir, "volunteer.csv") %>%
  detailed_entries(what = what, when = when, where = where, why = why, with = with)
```

## Awards and Honors

```{r}
read_tsv(paste0(data_dir, "awards.csv") %>%
  detailed_entries(what = what, when = when, where = where, why = why, with = with)
```

## Technical Skills

* Languages: R, Python, c++, bash
* Data visualization and reporting: ggplot2, shiny, plotly, rmarkdown, LaTeX
* Analysis and Machine learning: outlier detection, clustering, classification
* Software: git and github, RStudio, Sublime Text

## LANGUAGE SKILLS

* Spanish: First language
* English: Fluent, technical
* Hebrew: Fluent
* Japanese: Beginner
